### 2014-01-30 thesis/src/chapters/chapter-design.tex
Thesis: container as a resource

\section{Application manager}

\section{Application platform manager}
%w kazdej sekcji opis MAPEK - co monitoruje, w jaki sposob analizuje i planuje, wykonuje

@@

\begin{table}
  \centering
  \begin{tabular}{ c  c  c  c }
    \specialrule{.1em}{.05em}{.05em} 
    & \textbf{Full virtualization} & \textbf{OS-level virtualization} & \textbf{OS process} \\
    \specialrule{.1em}{.05em}{.05em} 
    Features &  &  & \\ \hline
    Examples &  &  & \\
    \hline
  \end{tabular}
  \caption{Containerisation technologies}
  \label{tab:containeristation-technologies}
\end{table}

@@

\subsubsection{Touchpoint}
Container's touchpoint externalises hypervisor and operating system APIs. Similarly to all touchpoints, two main parts can be distinguished:
\begin{itemize}
 \item \emph{sensors} - set of properties that expose system metrics such as CPU, memory, disk usage, network bandwidth - lista propertisow, charakterystyka (czy wymagane, co daja, dobra metryka?)
 \item \emph{effectors} - a collection of 'set' operations that aims to change container state: increase or decrease CPU or memory, for example. In fact, these operations directly corresponds to hypervisor capabilities. - lista wymagancych, + hypervisor, metryka
\end{itemize}

It is highly recommended for sensors and effectors to be linked, forming together manageability capabilities. In other words, property (i.e. CPU) can be read only when it is possible to set it as well.

>>>>

\section{Autonomic application manager}

\section{Autonomic application platform manager}
%w kazdej sekcji opis MAPEK - co monitoruje, w jaki sposob analizuje i planuje, wykonuje

@@

\begin{table}[!htbp]
  \centering
  \begin{tabularx}{\textwidth}[]{ X X X X }
    \specialrule{.1em}{.05em}{.05em} 
    & \textbf{Full virtualization} & \textbf{OS-level virtualization} & \textbf{OS process} \\
    \specialrule{.1em}{.05em}{.05em} 
    \textbf{Features} & 
-- complete simulation of machine's hardware

-- full isolation

-- host system is not shared among guests

    &
-- isolation is based on user-spaces

-- shared kernel

-- lesser overhead than full virutalization

-- effective i/o operations
    & 
-- custom solution that uses processes, cgroups, SELinux, for example

-- lesser overhead possible

\\ \hline
\textbf{Examples} &
-- KVM

-- Xen

-- VMware &

-- LXC

-- OpenVZ
&
-- OpenShift containers
\\ \hline
  \end{tabularx}
  \caption{Containerisation technologies}
  \label{tab:containeristation-technologies}
\end{table}

@@

\subsubsection{Touchpoint}
Container's touchpoint externalises hypervisor and operating system APIs. Similarly to all touchpoints, sensors for gathering data and effectors for influencing it can be distinguished. It is highly recommended for them to be linked, forming together manageability capabilities. In other words, property (i.e. CPU) can be read only when it is possible to set it as well. For instance, free / used CPU, free / used memory, network bandwidth, disk usage can be measured. Cloud-SAP requires free CPU to be at least supported.
